Online {\IterComp}

### 2017-11-16 related.tex
Mars et al in related work

Fursin~\etal~\cite{fursin07} attempted to find such a general approach. They proposed to use instructions per cycle (IPC)
as a metric for comparing different runs of the same program with different optimization settings and different inputs. Their hypothesis is
that application binaries displaying higher IPC are more efficient than lower IPC binaries. However, many optimization techniques affect
IPC in the opposite way, making the program more efficient while lowering IPC. The authors in~\cite{fursin07} acknowledge that this limits
the applicability of IPC for \itercomp. Our experiments in Section~\ref{sec:motivation} also show that IPC is not an appropriate metric
for quantifying efficiency for iterative compilation. In the context of multithreaded applications, IPC cannot be used to compare the performance of
different runs even when they use the same intput~\cite{alameldeen06,eyerman08}. Work-related metrics are shown to be more appropriate, but prior work
relied on application-specific work metrics. This paper presents the first automatic and application agnostic approach for deriving a work metric.

%PP: Discuss input sensitivity?

>>>>

Fursin~\etal~\cite{fursin07} attempted to find such a general approach. They proposed to use instructions per cycle (IPC)
as a metric for comparing different runs of the same program with different optimization settings and different inputs. Their hypothesis is
that application binaries displaying higher IPC are more efficient than lower IPC binaries. Similarly, Mars~\etal~\cite{Mars:2009:SBO:1545006.1545068}
propose using IPC for online adaptation. During the learning/monitoring phase, a small number of competing versions of a hot function are executed, each
for the same amount of time. The one with the highest number of retired instructions is selected for use.

However, many optimization techniques affect
IPC in the opposite way, making the program more efficient while lowering IPC. The authors in~\cite{fursin07} acknowledge that this limits
the applicability of IPC for \itercomp. Our experiments in Section~\ref{sec:motivation} also show that IPC is not an appropriate metric
for quantifying efficiency when the binary is changing. In the context of multithreaded applications, IPC cannot be used to compare the performance of
different runs even when they process the same input~\cite{alameldeen06,eyerman08}. Work-related metrics are shown to be more appropriate, but prior work
relied on application-specific work metrics. This paper presents the first automatic and application agnostic approach for deriving a work metric.
